### 2024-11-27 download-football-data.qmd
20241126 - calculate_stats() function from nflfastR

nfl_actualStats_seasonal_team <- nfl_actualStats_seasonal_team_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
load(file = "./data/nfl_actualStats_seasonal.RData")
```

>>>>

nfl_actualStats_seasonal_team <- nfl_actualStats_seasonal_team_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
```

```{r}
nfl_actualStats_seasonal_player %>% 
  group_by(player_id, season) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_seasonal_team %>% 
  group_by(team, season) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_actualStats_seasonal_player, nfl_actualStats_seasonal_team,
  file = "./data/nfl_actualStats_seasonal.RData"
)
```
